Dependent Object Types

### 2012-08-31 doc/candidacy/report.tex
typo

Now, we can emulate this Tribe example in Scala at the expense of some
synctactic overhead, since further binding and ``out'' selection are
not native. Emulating ``out'' faithfully involves a bit of hackery in
making Scala recognize that, for example, \code{e.from.type} is a
subtype of \code{e.out.Node}. As noted in the paper, using ``out'' in
library code obscures the symmetry between the parameters (for
example, in the \code{distance} method below) but allows the family
object to be recovered without being explicitly passed around
(contrast with the method \code{distance2}).
\lstinputlisting{tribe.scala}

>>>>

Now, we can emulate this Tribe example in Scala at the expense of some
syntactic overhead, since further binding and ``out'' selection are
not native. Emulating ``out'' faithfully involves a bit of hackery in
making Scala recognize that, for example, \code{e.from.type} is a
subtype of \code{e.out.Node}. As noted in the paper, using ``out'' in
library code obscures the symmetry between the parameters (for
example, in the \code{distance} method below) but allows the family
object to be recovered without being explicitly passed around
(contrast with the method \code{distance2}).
\lstinputlisting{tribe.scala}
